Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-14 Paper_presentation.tex
Table...

@@

>>>>

\begin{frame}

\item[\checkmark]The goal of the pre-warrant phase is not to make an arrest (a user, for example), but it is to obtain a judicially issued search warrant, for such cause (CP).

\item[\checkmark]This means, that we will look for a specify location, and not a person.

\item[\checkmark]Arrests in these criminal cases are typically not based on the network-acquired evidence. They are based on the fruits of the search and the person identified as possessing the contraband materials.

\begin{frame}

\item[\checkmark]Finally, we note that this follows a forensics model and
not the traditional security attacker model.

\item[\checkmark]The techniques can be applied very successfully even though there exist many ways to defeat them.

\item[\checkmark]But many people do not attempt to hide them, only change the name of the file, as we know to hide the word ''sexually'', but a intentionally name to be ease to discover the file for another peer.

@@

\item[\checkmark]We know that the strategies for removing content from the entire ecosystem (the internet) must target offenders from all countries.

\item[\checkmark]We do not have of a unified effort, and no such collaboration exists.

\item[\checkmark]Investigators need a triage strategy.

\item[\checkmark]The better were if the investigators have target to catch the more dangerous criminals, but such information is not available.

\begin{frame}

\item[\checkmark]In lieu of that ideal, investigators can take peers that are offensive in the net.

\item[\checkmark]Peers that show evidence the target of the intent the user.

\item[\checkmark]This includes peers that are online for the longest duration.

\item[\checkmark]Peers that share the largest number of ''FOI'' (File of Interest).

\item[\checkmark]Offenders by P2P network, as we know: eMule, Gnutella...or offender that seek to escape detection with the use of TOR.

\begin{frame}

\begin{block}{There are 6 (six) sub-groups of peers offenders:}

\begin{enumerate}

\item The top 10\% of GUID’s of largest corpora.

\item The top 10\% of GUID’s of sharing FOI the most numbers of days.

\item The top 10\% of GUID’s ranked contribuition metric (the same we saw in last topics).

\item The top 10\% of the set of GUID’s linked by ip adress sharing FOI.

\item The top 10\% of GUID’s that use a know TOR exit node.

\item The top 10\% of GUID’s  sharing FOI that use a IP adrres and we infer that is a non TOR relay.

\end{enumerate}

\begin{frame}
\begin{block}{We can see this  result under the table:}

\begin{table}

\centering

\caption{Sizes of each GUID subgroup}

\begin{tabular}{ccc}

\hline

Identifier & Gnutella & eMule \\

\hline
\hline
All GUIDs & 775,941 & 1,895,804 \\
Multi-Networks GUIDs & 84,925 (11\%) & 147,904 (7,8\%) \\
TOR GUIDs & 3,666 (0.47\%) & 16,290 (0.86\%) \\
TOR GUIDs (>2 days) & 2,592 (0.33\%) & 11,998 (0.63\%) \\
Relayed GUIDs & 76,478 (9.9\%) & 78,223 (4.1\%) \\
Top 10\% Observed & 84,235 (11\%) & 190,797 (10\%) \\
Top 10\% by Corpus & 77,782 (10\%) & 189,951 (10\%) \\
Top 10\% by Contribution & 77,595 (10\%) & 189,581 (10\%)\\

\hline
\end{tabular}
\label{table2}
\end{table}
